\documentclass[12pt, oneside]{article}

\usepackage{./texmf/preamble}

\graphicspath{{./assets/}}
\addglobalbib{sources.bib}

\onehalfspacing

\immediate\write18{texcount -merge \jobname.tex | sed -n 's/.*Words in text://p' | awk '{$1=$1};1' > 'build/count.txt'}

\providecommand{\totalwordcount}{\input{build/count.txt}}

% =================================================================
% Content
% =================================================================

\begin{document} % BEGIN
\pagestyle{frontmatter}

\begin{titlepage}
    \large

    \begin{center}

        \vspace*{2cm}

        {\bfseries
            IB Math Analysis and Approaches (HL) \\
            Extended Essay\\
            May 2024 Session}\\

        \vspace*{\fill}

        \rule{\linewidth}{1.5pt} \\ [0.5cm]
        {\LARGE \bfseries Mathematical Techniques and Applications of Camera Calibration }
        \rule{\linewidth}{0.5pt} \\

        \vspace*{\fill}

        \textbf{Research Question:} What mathematical techniques can be employed to develop highly accurate camera models, and what are their real-world applications where these models prove valuable? \\ [1cm]

        \textbf{Word Count:} \totalwordcount words

        \vspace*{2cm}

    \end{center}

\end{titlepage}

% =================================================================
\pagenumbering{roman}
\tableofcontents
% =================================================================
\clearpage
\pagestyle{mainmatter}
\pagenumbering{arabic}
\setcounter{page}{1}

\input{sections/intro}
\input{sections/approach}
\input{sections/prerequisites}
\input{sections/model}
\input{sections/solve}
\input{sections/extract}
\input{sections/experimental.tex}
\input{sections/applications}
% =================================================================

%TC:ignore
\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

I am very grateful to my supervisor Mr. Hoteit for his continual guidance and invaluable pieces of advice during the process of writing this extended essay. Additionally, I would like to express my appreciation to Mr. Auclair for dedicating his time to instruct me on camera operation and familiarizing me with camera settings. I am also indebted to Mr. Matthewson for his guidance with the manufacturing of my calibration object, and to Leon, for his help in operating the laser cutter. Last but not least, I want to thank to Aditya for aiding me with the creation of a diagram used in my paper.
\clearpage
\pagestyle{backmatter}

\printbibliography[heading=bibintoc]{}

% =================================================================

\clearpage
\begin{appendices}
    \pagestyle{appendices}
    \input{sections/appendix/data}
    \input{sections/appendix/object}
    \input{sections/appendix/code}
\end{appendices}
%TC:endignore

\end{document} % END

