\section{Introduction}

Camera calibration, also known as camera resectioning, is the process of determining the intrinsic and extrinsic parameters of a camera. The knowledge of the accurate values of these values parameters are essential, as it enables us to create a mathematical model which describes how a camera projects 3D points from a scene onto the 2D image it captures. The intrinsic parameters deal with the camera's internal characteristics, while the extrinsic parameters describe its position and orientation in the world. The importance of a well-calibrated camera becomes very apparent in photogrammetric applications, where precise measurements of 3-dimensional physical objects are derived from photographic images.

Photogrammetry, as a comprehensive science in its own right, concerns itself with obtaining accurate measurements of 3-dimensional physical objects through photographic imagery. Photogrammetry was first employed by Prussian architect Albrecht Meydenbauer in the 1860s, who used photogrammetric techniques to create some of the most detailed topographic plans and elevations drawings \footcite[][1]{albertzLookBack2007}. Today, photogrammetric techniques are used in a multitude of applications spanning diverse fields, including but not limited to: computer vision, topographical mapping, medical imaging, and forensic analysis. 

While camera calibration is essential in ensuring the accuracy of photogrammetric applications, it itself also relies on these very same photogrammetric techniques in order to estimate these parameters. This underscores the essential relationship between photogrammetry and camera calibration. In essence, the developments of photogrammetry and camera calibration are closely intertwined, and this shows the importance of understanding and accurately determining a camera's intrinsic and extrinsic parameters for various applications.

\subsection{Problem Statement}

While manufacturers of cameras often report parameters of cameras, such as the nominal focal length and pixel sizes of their camera sensor, these figures are typically approximations which can vary from camera to camera, particularly in consumer-grade cameras. As such, the use of these estimates by manufacturers are unsuitable in developing camera models for applications requiring high accuracy. Combined with the potential for manufacturing defects as well as unknown lens distortion coefficients further necessitates the need for a reliable method for determining the parameters of a camera. 

Camera calibration emerges as the answer to these problems, allowing us to create very accurate estimates for the parameters of a camera. As such, it is important that we ac

 







Importance of reserach question

In order to accurately determine the position of 3D points based on data from multiple 2D images, we must have knowledge of the parameters of the camera.

This process of calculating








